---
title: "Findings 3"
weight: 3
draft: false
output: html_document
---

```{css, echo=FALSE}
/* this chunnk of code centers all of the headings */
h1, h2, h3 {
  text-align: center;
}
```

##Modeling Census Tract Level Evictions: Visualization of socio-demographic variables and eviction rates in Richmond 2013-2018

To provide further guidance for policymakers interested in understanding evictions in Richmond, we provide a dashboard that can be used to visualize the socio-demographic variables that our statistical model identified as being associated with eviction rates. This dashboard provides some context for what we can observe about the city of Richmond and the variation across census tracts and time.

### Embedded Shiny Apps

In the visualization below, we have eviction filings between Jan-May 2020. This temporal maps give us an idea about how eviction filing changed due the COVID pandemic. We can see that after March eviction filings dropped drastically. 

```{r, echo=FALSE, fig.height=15, fig.fullwidth=TRUE}
knitr::include_app('https://afrina.shinyapps.io/Shiny_eviction_2020/', height="610px")

```

In the visualization below we have the Socio-Demographic Factors used in the regression model over time (2013-2018).

```{r, echo=FALSE, fig.fullwidth=TRUE}
knitr::include_app('https://tabassum.shinyapps.io/Model_Variables/', height="750px")
  
```
In the visualization below, we have the eviction rate at the census tract level from 2000-2016.
```{r, echo=FALSE, fig.fullwidth=TRUE}
knitr::include_app('https://afrina.shinyapps.io/Shiny_Eviction_Rate/', height="615px")
  
```

In the visualization below, we have the median housing price at the census tract level from 2000-2018.
```{r, echo=FALSE, fig.fullwidth=TRUE}
knitr::include_app('https://wellay01.shinyapps.io/ShinyRichmond/', height="615px")
  
```

[Continue to Conclusion](https://boya66.github.io/Richmond_website/findings/results-section-four/)
