---
title: "Findings 3"
tags: ["R", "geospatial", "app"]
weight: 3
draft: false
output: html_document
---

```{css, echo=FALSE}
/* this chunnk of code centers all of the headings */
h1, h2, h3 {
  text-align: center;
}
```

##Modeling Census Tract Level Evictions: Visualization of socio-demographic variables and eviction rates in Richmond 2013-2018

In the visualization below, we have an eviction indicator for census tracts in the city of Richmond.

```{r, echo=FALSE, fig.fullwidth=TRUE}
knitr::include_app('https://tabassum.shinyapps.io/residual_inference/')
```

### Embedded Shiny Apps

In the visualization below, we have eviction filings between Jan-May 2020. This temporal maps give us an idea about how eviction filing changed due the COVID pandemic. We can see that after March eviction filings dropped drastically. 

```{r, echo=FALSE, fig.fullwidth=TRUE}
knitr::include_app('https://afrina.shinyapps.io/Shiny_eviction_2020/')
```

In the visualization below we have the Socio-Demographic Factors used in the regression model over time (2013-2018).

```{r, echo=FALSE, fig.fullwidth=TRUE}
knitr::include_app('https://tabassum.shinyapps.io/Model_Variables/')
  
```
In the visualization below, we have the eviction rate at the census tract level from 2000-2016.
```{r, echo=FALSE, fig.fullwidth=TRUE}
knitr::include_app('https://afrina.shinyapps.io/Shiny_Eviction_Rate/')
  
```

In the visualization below, we have the median housing price at the census tract level from 2000-2018.
```{r, echo=FALSE, fig.fullwidth=TRUE}
knitr::include_app('https://wellay01.shinyapps.io/ShinyRichmond/')
  
```

[Continue to References](https://boya66.github.io/Richmond_website/findings/references/)
